\item[1983 SCF] The 1983 SCF did not ask about the investment strategy or risk characteristics of mutual funds or retirement accounts, so we had to make educated guesses based on other information.  Tax-free mutual funds were allotted to the 'fairly safe' category because such funds consist almost exclusively of state and local government bonds, direct holdings of which we put in this category.  Taxable mutual funds were allotted to the 'risky' category, because in the early 1980s these funds typically contained a mix of stocks and bonds.  The calculation of risky, clearly safe, and fairly safe defined contribution pensions uses the institution that held the IRA/Keogh accounts as a proxy for investment direction.  If a real estate investment company held the accounts, then those defined contribution pensions were considered risky.  If a commercial bank, savings and loan, or credit union held the accounts, then those assets were considered fairly safe.  If a brokerage, insurance company, employer, school/college/university, investment management company, or the AARP held the accounts, the defined contribution pensions were split 50/50 between the fairly safe and risky.  In the case that the household had no IRA/Keogh accounts, but had a thrift pension account, the assets were considered fairly safe.\item[1989-1995 SCF] These surveys asked about the investment strategy for mutual funds and retirement accounts.  Funds and accounts that consisted exclusively of one category of asset (such as stock or bond mutual funds) we allocated in the same way that we allocated direct holdings of that asset type.  Mutual funds and accounts that contained a mix of stocks and safe or fairly safe bonds were allocated half-and-half to the 'fairly safe' and 'risky' categories.  Accounts invested in real estate, commodities or limited partnerships were put in the `risky' category.
